
\begin{frame}{Problem 1}
\begin{scriptsize}
Define a class \texttt{Boy} that keeps information for name, surname and years.
Define the needed constructors and method for printing in format:
\\Boy: [Name] [Surname] [Years].

Define a class \texttt{Girl} with the same attributes as Boy but with different
printing format:
\\Girl: [Name] [Surname] [Years].

Define a class \texttt{Date} that contains one Girl and one Boy. Implement the
function \texttt{print()} that will print the info of the date in the following
format:
\\Date: Boy: [Name] [Surname] [Years], Girl: [Name] [Surname] [Years].

Write a function \texttt{areMatch()} that will return true if their age
difference is less than 10 and the sum of the length of their names is even
number, otherwise false.
\end{scriptsize}
\end{frame}

\begin{frame}[fragile]{Problem 1}{Solution 1/3}
\lstinputlisting[lastline=32]{src/av4/p41.cpp}
\end{frame}

\begin{frame}[fragile]{Problem 1}{Solution 2/3}
\lstinputlisting[firstline=34,lastline=52]{src/av4/p41.cpp}
\end{frame}

\begin{frame}[fragile]{Problem 1}{Solution 3/3}
\lstinputlisting[firstline=54]{src/av4/p41.cpp}
\end{frame}


\begin{frame}{Problem 2}
\begin{scriptsize}
Define a class \texttt{Team} that keeps information about the name, year formed
and the host city. Define a class \texttt{Game} that contains info for the home
and guest teams (objects from class \texttt{Team}), goals scored by the home
team, and goals scored by the guest team.

Define separate function that accepts as arguments two objects from the class
\texttt{Game} and checks if the second game is return match (the both teams are
the same with reverse order). The the both games are return match, than should
return the team that is winner on agregate, otherwise should print message that
the games are not return match and return NULL.

\end{scriptsize}
\end{frame}

\begin{frame}[fragile]{Problem 2}{Solution 1/3}
\lstinputlisting[lastline=26]{src/av4/p42.cpp}
\end{frame}

\begin{frame}[fragile]{Problem 2}{Solution 2/3}
\lstinputlisting[firstline=28, lastline=58]{src/av4/p42.cpp}
\end{frame}

\begin{frame}[fragile]{Problem 2}{Solution 3/3}
\lstinputlisting[firstline=59]{src/av4/p42.cpp}
\end{frame}

\begin{frame}{Problem 3}
\begin{scriptsize}
Define a class \texttt{Date} that will keep day, month and year (int). Than
implement a class \texttt{Employee} that has name (max 20 chars), sallary and
date of birth (object from class Date). Implement two functions that accept
arguments array of Employee objects and their number. First function should
return the employee with largest sallary, and the second one should return the
youngest employee.

Write a main function that will test these classes and functions.
\end{scriptsize}
\end{frame}

\begin{frame}[fragile]{Problem 3}{Solution 1/3}
\lstinputlisting[lastline=25]{src/av4/p43.cpp}
\end{frame}
\begin{frame}[fragile]{Problem 3}{Solution 2/3}
\lstinputlisting[firstline=27,lastline=51]{src/av4/p43.cpp}
\end{frame}
\begin{frame}[fragile]{Problem 3}{Solution 3/3}
\lstinputlisting[firstline=54]{src/av4/p43.cpp}
\end{frame}
