%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Content starts here %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Problem 1}
Write a programm that will compare two dates (day, month, year) and will compute
the difference in days between them. Implement the computations in separate
functions.\\
\emph{Define a struct for date} \texttt{date}.
\end{frame}

\begin{frame}[fragile]{Problem 1}{Solution 1/3}
\lstinputlisting[lastline=9]{src/av1/z1.c}
\end{frame}

\begin{frame}[fragile]{Problem 1}{Solution 2/3}
\lstinputlisting[firstline=11,lastline=30]{src/av1/z1.c}
\end{frame}

\begin{frame}[fragile]{Problem 1}{Solution 3/3}
\lstinputlisting[firstline=32]{src/av1/z1.c}
\end{frame}

\begin{frame}{Problem 2}
Write a program that will comptute the vector and the scalar product of two
vectors. Vectors are represented with coordinates in threedimensional
Cartesian coordinate system. Compute the products in separate functions.\\
\emph{Define a struct for vector named} \texttt{vector}.
\end{frame}

\begin{frame}[fragile]{Problem 2}{Solution 1/2}
\lstinputlisting[lastline=21]{src/av1/z2.c}
\end{frame}

\begin{frame}[fragile]{Problem 2}{Solution 2/2}
\lstinputlisting[firstline=23]{src/av1/z2.c}
\end{frame}

\begin{frame}{Problem 3}
Write a struct for representing complex numbers. Then implement functions for
addition, substruction and multiplication of two complex numbers. Test the
functions in a main program where you read two complex numbers from standard
input.
\end{frame}

\begin{frame}[fragile]{Problem 3}{Solution 1/3}
\lstinputlisting[lastline=20]{src/av1/z3.c}
\end{frame}

\begin{frame}[fragile]{Problem 3}{Solution 2/3}
\lstinputlisting[firstline=22,lastline=33]{src/av1/z3.c}
\end{frame}

\begin{frame}[fragile]{Problem 3}{Solution 3/3}
\lstinputlisting[firstline=35]{src/av1/z3.c}
\end{frame}

\begin{frame}{Problem 4}
Read from standard input data for unknown number of students. Each row of the
data is in following format:
\begin{itemize}
  \item first name
  \item last name
  \item number (format xxyzzzz)
  \item four numbers (points for each problem)
\end{itemize}         
     separated with tab space.\\
Write a program that will print list of students, where each row will have: last
name, first name, number, and total points sorted by the number of points. BTW
the names should be printed with first capital letter.
\end{frame}

\begin{frame}[fragile]{Problem 4}{Solution 1/3}
\lstinputlisting[lastline=16]{src/av1/z4.c}
\end{frame}

\begin{frame}[fragile]{Problem 4}{Solution 2/3}
\lstinputlisting[firstline=18,lastline=28]{src/av1/z4.c}
\end{frame}

\begin{frame}[fragile]{Problem 4}{Solution 3/3}
\lstinputlisting[firstline=30]{src/av1/z4.c}
\end{frame}


\begin{frame}{Problem 5}
Write a program that will read from standard input data for countries and will
print on the standard output the name of the president of the country whose
capital has largest population.
\begin{itemize}
  \item Data for country: name, president, capital and population
  \item Data for city: name and population
  \item Data for president: name, political party
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Problem 5}{Solution 1/2}
\lstinputlisting[lastline=19]{src/av1/z5.c}
\end{frame}

\begin{frame}[fragile]{Problem 5}{Solution 2/2}
\lstinputlisting[firstline=20]{src/av1/z5.c}
\end{frame}

\begin{frame}{Homework}
Modify problem 4 so the struct for student has an array of subjects (not more
than 10) with grades from exams. Write a program that will print list of
students sorted by their avarage grade in descending order. Data for the subject
is: name of the subject and grade.
\end{frame}
