%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Content starts here %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{Defining class and object}
\begin{exampleblock}{Difining class}
\begin{lstlisting}
class Class_name {
private:
    /* variables and methods not visible outside of class*/ 
public:
    /* variables and methods visible outside of class*/ 
};
\end{lstlisting}
\end{exampleblock}
\begin{exampleblock}{Instantiating object}
\begin{lstlisting}
Class_name object_name;
\end{lstlisting}
\end{exampleblock}
\end{frame}

\begin{frame}[fragile,shrink=10]{Defining class}{Example}
\lstinputlisting{src/av3/ex1.cpp}
\end{frame}

\begin{frame}{Objects lifecycle}
\begin{enumerate}
  \item Constructor - special method of each class which is called always when
  an object of the class is created (instantiated)
  \item Destructor - special method of each class which is called to free
  the memory that the instantiated object allocated
\end{enumerate}
\end{frame}

\begin{frame}{Problem 1}{Triangle class}
Write a class for geometric figure triangle. In the class implement methods for
computing the area and perimeter of the triangle.\\
Than write a main function where you will instantiate one object of this class
with values read from SI. Call the methods of this object for computing area
and perimeter.
\end{frame}

\begin{frame}[fragile]{Problem 1}{Solution 1/2 (class)}
\lstinputlisting[lastline=27]{src/av3/z1.cpp}
\end{frame}

\begin{frame}[fragile]{Problem 1}{Solution 2/2 (main)}
\lstinputlisting[firstline=28]{src/av3/z1.cpp}
\end{frame}

\begin{frame}{Problem 2}{Employee class}
Write a class that will keep data for one employee:
\begin{itemize}
  \item name
  \item sallary
  \item position (position can be employee, manager, owner)
\end{itemize}
Write a main function where from SI you will read data for N employees, and then
print a list of employees sorted in descending order by the sallary.
\end{frame}

\begin{frame}[fragile]{Problem 2}{Solution 1/4}
\lstinputlisting[lastline=26]{src/av3/z2.cpp}
\end{frame}

\begin{frame}[fragile]{Problem 2}{Solution 2/4}
\lstinputlisting[firstline=28,lastline=46]{src/av3/z2.cpp}
\end{frame}

\begin{frame}[fragile]{Problem 2}{Solution 3/4}
\lstinputlisting[firstline=48,lastline=58]{src/av3/z2.cpp}
\end{frame}

\begin{frame}[fragile]{Problem 2}{Solution 4/4}
\lstinputlisting[firstline=60]{src/av3/z2.cpp}
\end{frame}

\begin{frame}{Problem 3}{E-mail class}
Write a class that describes an e-mail message. The class should implement
method for showing the contents of the message on the screen.\\
Then write a main function where the parameters of the message are read from SI
and an object of this class is instantiated. Then call the method for printing
the message. The validity of the e-mail address should be checked the existance
of the @ character.
\end{frame}

\begin{frame}[fragile]{Problem 3}{Solution 1/4}
\lstinputlisting[lastline=24]{src/av3/z3.cpp}
\end{frame}

\begin{frame}[fragile]{Problem 3}{Solution 2/3}
\lstinputlisting[firstline=25,lastline=52]{src/av3/z3.cpp}
\end{frame}

\begin{frame}[fragile]{Problem 3}{Solution 3/3}
\lstinputlisting[firstline=53]{src/av3/z3.cpp}
\end{frame}

% \begin{frame}[fragile]{Problem 4}{Класа за комплексни броеви}
% \lstinputlisting[lastline=21]{src/av3/z4.cpp}
% \end{frame}

% \begin{frame}[fragile]{Problem 4}{Преоптоварување на оператори
% \texttt{+=, -=, *=, /=}}
% \lstinputlisting[firstline=22,lastline=43]{src/av3/z4.cpp}
% \end{frame}
% 
% \begin{frame}[fragile]{Problem 4}{Преоптоварување на оператори
% \texttt{+, -, *, /}}
% \lstinputlisting[firstline=61,lastline=76]{src/av3/z4.cpp}
% \end{frame}
% 
% \begin{frame}[fragile]{Problem 4}{Преоптоварување на оператори
% \texttt{<<, >>}}
% \lstinputlisting[firstline=44,lastline=59]{src/av3/z4.cpp}
% \end{frame}
% 
% \begin{frame}[fragile]{Problem 4}{Главна функција}
% \lstinputlisting[firstline=77]{src/av3/z4.cpp}
% \end{frame}
